---
params:
  team: ATL
  set_title: Atlanta Falcons
title: "`r params$set_title`"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
library(tidyverse)
library(hrbrthemes)
library(patchwork)
library(knitr)
library(kableExtra)
library(lubridate)
theme_set(theme_ipsum_rc())
update_geom_font_defaults(font_rc_light)
options(htmltools.dir.version = FALSE)
opts_chunk$set(fig.retina=2)
```

```{r load_files, include=FALSE}
source('fb_viz.R')
source('utils.R')
source('writing_utils.R')

nfl <- read_rds('data/nfl_last5_stats.rds')
team_df <- nfl %>% filter(team == params$team)

details <- read_csv('data/team_details.csv')
tm_details <- filter(details, abrv == params$team)

team_colors <- read_rds('data/nfl_colors.rds')

tm_pal <- filter(team_colors,
                 team == params$team) %>%
  unnest(colors) %>%
  pull(colors)

big_four <- read_rds('data/big_four_ranks.rds')
big_four_team <- filter(big_four, team == params$team)

rank_data <- read_rds('data/nfl-2018-stats-ranks.rds')
```

```{r data_trans, include=FALSE}
vs_div <- team_df %>% 
  filter(conf_game == 1, div_game == 1) %>% 
  summarise_at(vars(ats_w:su_p),sum)
vs_conf <- team_df %>% 
  filter(conf_game == 1) %>% 
  summarise_at(vars(ats_w:su_p),sum)
ats <- make_ats_sum_tbl(nfl)
home_away_records <- get_location_records(team_df)

make_img_path <- function(name){
  glue::glue(
  'nfl_logos/{tname}_logo.png',
  tname=str_replace_all(name, ' ', '_'))
}

img_path <- make_img_path(tm_details$fullname)
```

```{r logo, echo=FALSE, out.width = "40%"}
include_graphics(img_path)
```

## Team Info

| |
| --- | ---
|Team | `r tm_details$fullname`
|Conference |  `r tm_details$conf`
|Division |  `r tm_details$div`
|Stadium |  `r tm_details$stad`
|`r year(today())` Coach | `r tm_details$coach`

`r get_team_rank_article(tm_details, big_four_team)`

## Past 5 Seasons ATS vs All Opponents

*All stats and records for the regular season only.*

```{r five_yr_rslts, echo=FALSE}
make_results_tbl(team_df) %>% 
  kable(align = 'c')
```

```{r su_results_plot, echo=FALSE}
make_su_results_plot(ats, params$team, tm_pal) +
  labs(subtitle = 'Regular Season Results')
```

```{r ats_results_plot, echo=FALSE}

make_ats_results_plot(ats, params$team, tm_pal) +
  labs(subtitle = 'ATS Results')
```

```{r ou_results_plot, echo=FALSE}
make_ou_results_plot(ats, params$team, tm_pal) +
  labs(subtitle = 'Over/Under Results')

```

## Conference and Division Records

Over the last five seasons, the `r tm_details$fullname` are `r make_team_records(vs_conf$su_w, vs_conf$su_l, vs_conf$su_p)` against conference opponents and `r make_team_records(vs_div$su_w, vs_div$su_l, vs_div$su_p)` vs division opponents. 

### vs Division Opponents ATS by Team

```{r conf_div_tbl, echo=FALSE}
team_df %>% 
  filter(conf_game == 1, div_game == 1) %>% 
  group_by(opp) %>% 
  summarise_at(vars(ats_w:su_p),sum) %>% 
  ungroup() %>% 
  div_results_tbl() %>% 
  kable(align = 'c')
```

### `r tm_details$conf` Games

```{r conf_game_ats, echo=FALSE}
team_df %>% 
  filter(conf_game == 1) %>% 
  make_results_tbl() %>% 
  kable(align = 'c')
```

### `r paste(tm_details$conf, tm_details$div)` Games

```{r div_games_ats, echo=FALSE}
team_df %>% 
  filter(div_game == 1) %>% 
  make_results_tbl() %>% 
  kable(align = 'c')
```

## Team Performance vs ATS & OU Lines

```{r ats_ou_scatter_plot, echo=FALSE}
p1 <- sprd_vs_mov_plot(team_df, tm_pal) +
  labs(subtitle = 'Point Spread vs MOV')
p2 <- tot_vs_score_plot(team_df, tm_pal) +
  labs(subtitle = 'O/U vs Final Score')

p1 + p2
```

## ATS Records by Location

```{r by_location_ats, echo=FALSE, fig.cap="Over last 5 seasons"}
location_ats_tbl(team_df) %>% 
  kable(align = 'c')
```

## Weekly Performance ATS by Week

```{r by_wk_heatmap, echo=FALSE, fig.cap="Over last 5 seasons"}
week_heatmap_plot(team_df, tm_pal)
```

## Team Scoring Last 5 Seasons

```{r ppg_plot, echo=FALSE}
make_ppg_plot(nfl, params$team, tm_pal) +
  labs(subtitle = 'Team and Opponent Avg Points Scored per Game')
```

## `r max(team_df$seas)` Season at a Glance

In `r as.character(max(team_df$seas))` the `r tm_details$fullname`:

`r season_bullet_points(tm_details, home_away_records)`

## 2018 Schedule and Results

```{r seas_schd, echo=FALSE}
team_df %>% 
  get_schd() %>% 
  kable(align = 'c')
```


`r in_close_games(filter(team_df, seas == '2018'), tm_details)`
`r pythag_proj_txt(team_df, tm_details)`


## Offensive Stats

### Avg Points per Quarter Scored

```{r pts_per_qtr_off, echo=FALSE}

tmp_off <- team_df %>% 
    filter(seas == 2018) %>% 
    select(team, seas, q1p_tm:q4p_tm, q1p_opp:q4p_opp) %>% 
    gather(qtr, scr, -team, -seas) %>% 
    group_by(seas, qtr) %>% 
    summarise(scr = mean(scr)) %>% 
    ungroup() %>% 
    separate(qtr, into = c('qtr', 'who'), sep = '_') %>% 
    mutate(qtr = factor(qtr, 
                        levels = c('q1p','q2p','q3p','q4p'),
                        labels = c('Q1','Q2','Q3','Q4'))) %>% 
    filter(who == 'tm') 

point_qtr_dist(tmp_off, tm_pal)
```

`r mk_off_tbl(big_four_team)`

## Defensive Stats

### Avg Points Allowed per Quarter 

```{r pts_per_qtr_def, echo=FALSE}
tmp_def <- team_df %>% 
    filter(seas == 2018) %>% 
    select(team, seas, q1p_tm:q4p_tm, q1p_opp:q4p_opp) %>% 
    gather(qtr, scr, -team, -seas) %>% 
    group_by(seas, qtr) %>% 
    summarise(scr = mean(scr)) %>% 
    ungroup() %>% 
    separate(qtr, into = c('qtr', 'who'), sep = '_') %>% 
    mutate(qtr = factor(qtr, 
                        levels = c('q1p','q2p','q3p','q4p'),
                        labels = c('Q1','Q2','Q3','Q4'))) %>% 
    filter(who == 'opp') 

point_qtr_dist(tmp_def, tm_pal)
```

`r mk_def_tbl(big_four_team)`

## Point Differential per Quarter

```{r pt_diff_plot, echo=FALSE}
pt_diff_plot(nfl, params$team, tm_pal) 
```

## Predictive Team Stats

```{r pred_tm_stats, echo=FALSE, warning=FALSE, message=FALSE}
proper_stat_names <- tibble(
    stat = c('f1d', 'fgm', 'td', 'top', 'tovrtds'),
    statistic = c(
      'FirstDowns',
      'FieldGoals',
      'TouchDowns',
      'TimeOfPoss',
      'TDsOffTurnovrs'
    )
  )

clean_ranks <- rank_data %>%
  filter(team == params$team) %>%
  select(-team) %>%
  gather(stat, val) %>%
  mutate(
    who = ifelse(grepl(x = stat, pattern = '_tm'), 'tm', 'opp'),
    is_rank = ifelse(grepl(x = stat, pattern = '_rank'), 'rank', 'stat'),
    stat = str_remove_all(stat, '_tm') %>%
      str_remove_all('_opp') %>%
      str_remove_all('_rank')
  )

clean_ranks <- clean_ranks %>%
  left_join(proper_stat_names) %>%
  select(-stat)

clean_rank_sprd <- clean_ranks %>%
  group_by(who) %>%
  spread(is_rank, val) %>%
  filter(who == 'tm') %>%
  select(Statistic = statistic,
         AvgPerGame = stat,
         Rank = rank,
         -who)

clean_rank_sprd %>%
  ungroup() %>% 
  select(-who) %>% 
  mutate(AvgPerGame = ifelse(
    Statistic == 'TimeOfPoss',
    paste0(round(AvgPerGame * 100), '%'),
    AvgPerGame %>% round(2)
  )) %>%
  kable(align = 'c')
```

## Predictive Opponent Stats

```{r pred_opp_stats, echo=FALSE, warning=FALSE, message=FALSE}
proper_stat_names <- tibble(
    stat = c('f1d', 'fgm', 'td', 'top', 'tovrtds'),
    statistic = c(
      'FirstDowns',
      'FieldGoals',
      'TouchDowns',
      'TimeOfPoss',
      'TDsOffTurnovrs'
    )
  )

clean_ranks <- rank_data %>%
  filter(team == params$team) %>%
  select(-team) %>%
  gather(stat, val) %>%
  mutate(
    who = ifelse(grepl(x = stat, pattern = '_tm'), 'tm', 'opp'),
    is_rank = ifelse(grepl(x = stat, pattern = '_rank'), 'rank', 'stat'),
    stat = str_remove_all(stat, '_tm') %>%
      str_remove_all('_opp') %>%
      str_remove_all('_rank')
  )

clean_ranks <- clean_ranks %>%
  left_join(proper_stat_names) %>%
  select(-stat)

clean_rank_sprd <- clean_ranks %>%
  group_by(who) %>%
  spread(is_rank, val) %>%
  filter(who == 'opp') %>%
  select(Statistic = statistic,
         AvgPerGame = stat,
         Rank = rank,
         -who)

clean_rank_sprd %>%
  ungroup() %>% 
  select(-who) %>% 
  mutate(AvgPerGame = ifelse(
    Statistic == 'TimeOfPoss',
    paste0(round(AvgPerGame * 100), '%'),
    AvgPerGame %>% round(2)
  )) %>%
  kable(align = 'c')
```
