---
params:
  team: ATL
  set_title: Atlanta Falcons
title: "`r params$set_title`"
output:
  md_document:
    variant: gfm
---

```{r setup, include=FALSE}
source('load_libs.R')
theme_set(theme_ipsum_rc())
update_geom_font_defaults(font_rc_light)
options(htmltools.dir.version = FALSE)
opts_chunk$set(fig.retina=2)
```

```{r load_files, include=FALSE}
source('load_libs.R')
source('scripts/utils.R')

input_stats <- 'processed_data/stats_10y_seas.rds'
input_details <- 'processed_data/team_information.rds'
input_bigfour <- 'processed_data/big_four_ranks.rds'
input_ranks <- 'processed_data/nfl-2018-stats-ranks.rds'


# team_filter <- partial(.f = filter, team == params$team)

team_df <- read_rds(input_stats) %>% 
  filter(team == params$team)

details <- read_rds(input_details) %>% 
  filter(abrv == params$team)
  
tm_pal <- details %>% 
  pull(colors) %>% 
  unlist()

big_four_team <- read_rds(input_bigfour) %>% 
  filter(team == params$team)
rank_data <- read_rds(input_ranks)


ats <- make_regseas_ats_sum_tbl(team_df)
last_seas <- max(team_df$seas)
bet_types <- list(su = c('W','L','P'),
                  ats = c('W','L','P'),
                  ou = c('O', 'U', 'P'))
proper_stat_names <- tibble(
    stat = c('f1d', 'fgm', 'td', 'top', 'tovrtds'),
    statistic = c(
      'FirstDowns',
      'FieldGoals',
      'TouchDowns',
      'TimeOfPoss',
      'TDsOffTurnovrs'
    )
  )

vs_div <- team_df %>% 
  get_div_games() %>% 
  sum_up_records()
vs_conf <- team_df %>% 
  get_conf_games() %>% 
  sum_up_records()
ats <- make_regseas_ats_sum_tbl(team_df)
home_away_records <- get_location_records(team_df, last_seas)

rm(input_stats, input_ranks, input_bigfour, input_details)
```


```{r logo, echo=FALSE, out.width = "40%"}
include_graphics(details$logo)
```

## Team Info

| |
| --- | ---
|Team | `r details$name`
|Conference |  `r details$conf`
|Division |  `r details$div`
|Stadium |  `r details$stad`
|`r year(today())` Coach | `r details$coach`

`r get_team_rank_article(details, big_four_team)`

## Past 10 Seasons ATS vs All Opponents

*All results for the regular season only.*

```{r five_yr_rslts, echo=FALSE}
team_df %>% 
  filter(wk <= 17) %>% 
  make_results_tbl() %>% 
  kable(align = 'c')
```

```{r su_results_plot, echo=FALSE}
make_results_plot(ats, tm_pal, 'su', bet_types$su) +
  labs(subtitle = 'Regular Season Results')
```

```{r ats_results_plot, echo=FALSE}
make_results_plot(ats, tm_pal, 'ats', bet_types$ats) +
  labs(subtitle = 'ATS Results')
```

```{r ou_results_plot, echo=FALSE}
make_results_plot(ats, tm_pal, 'ou', bet_types$ou) +
  labs(subtitle = 'Over/Under Results')
```

## Conference and Division Records

Over the last five seasons, the `r details$name` are `r make_team_records(vs_conf$su_w, vs_conf$su_l, vs_conf$su_p)` against conference opponents and `r make_team_records(vs_div$su_w, vs_div$su_l, vs_div$su_p)` vs division opponents. 

### vs Division Opponents ATS by Team

```{r conf_div_tbl, echo=FALSE}
team_df %>% 
  get_div_games() %>% 
  group_by(opp) %>% 
  sum_up_records() %>% 
  ungroup() %>% 
  div_results_tbl() %>% 
  kable(align = 'c')
```

### `r details$conf` Games

```{r conf_game_ats, echo=FALSE}
team_df %>% 
  get_conf_games() %>% 
  make_results_tbl() %>% 
  kable(align = 'c')
```

### `r paste(details$conf, details$div)` Games

```{r div_games_ats, echo=FALSE}
team_df %>% 
  get_div_games() %>% 
  make_results_tbl() %>% 
  kable(align = 'c')
```

## Team Performance vs ATS & OU Lines

```{r ats_ou_scatter_plot, echo=FALSE}
p1 <- sprd_vs_mov_plot(team_df, tm_pal) +
  labs(subtitle = 'Point Spread vs MOV')
p2 <- tot_vs_score_plot(team_df, tm_pal) +
  labs(subtitle = 'O/U vs Final Score')

p1 + p2
```

## ATS Records by Location

```{r by_location_ats, echo=FALSE}
location_ats_tbl(team_df) %>% 
  kable(align = 'c')
```

## Weekly Performance ATS by Week

```{r by_wk_heatmap, echo=FALSE}
week_heatmap_plot(team_df, tm_pal)
```

## Team Scoring Last 10 Seasons

```{r ppg_plot, echo=FALSE}
make_ppg_plot(team_df, tm_pal) +
  labs(subtitle = 'Team and Opponent Avg Points Scored per Game')
```

## `r max(team_df$seas)` Season at a Glance

In `r as.character(max(team_df$seas))` the `r details$name`:

`r season_bullet_points(details, home_away_records)`



## `r last_seas` Schedule and Results

```{r seas_schd, echo=FALSE}
team_df %>% 
  get_schd(last_seas) %>% 
  kable(align = 'c')
```


`r in_close_games(filter(team_df, seas == '2018'), details)`
`r pythag_proj_txt(team_df, details)`

## Offensive Stats

### Avg Points per Quarter Scored

```{r pts_per_qtr_off, echo=FALSE}

tmp_off <- team_df %>% 
    select(team, seas, q1p_tm:q4p_tm, q1p_opp:q4p_opp) %>% 
    gather(qtr, scr, -team, -seas) %>% 
    group_by(seas, qtr) %>% 
    summarise(scr = mean(scr)) %>% 
    ungroup() %>% 
    separate(qtr, into = c('qtr', 'who'), sep = '_') %>% 
    mutate(qtr = factor(qtr, 
                        levels = c('q1p','q2p','q3p','q4p'),
                        labels = c('Q1','Q2','Q3','Q4'))) %>% 
    filter(who == 'tm') 

point_qtr_dist(tmp_off, tm_pal)
```

`r mk_off_tbl(big_four_team)`## Defensive Stats

### Avg Points Allowed per Quarter 

```{r pts_per_qtr_def, echo=FALSE}
tmp_def <- team_df %>% 
    select(team, seas, q1p_tm:q4p_tm, q1p_opp:q4p_opp) %>% 
    gather(qtr, scr, -team, -seas) %>% 
    group_by(seas, qtr) %>% 
    summarise(scr = mean(scr)) %>% 
    ungroup() %>% 
    separate(qtr, into = c('qtr', 'who'), sep = '_') %>% 
    mutate(qtr = factor(qtr, 
                        levels = c('q1p','q2p','q3p','q4p'),
                        labels = c('Q1','Q2','Q3','Q4'))) %>% 
    filter(who == 'opp') 

point_qtr_dist(tmp_def, tm_pal)
```

`r mk_def_tbl(big_four_team)`
## Point Differential per Quarter

```{r pt_diff_plot, echo=FALSE}
pt_diff_plot(team_df, details, params$team, tm_pal) 
```

## Predictive Team Stats

```{r pred_tm_stats, echo=FALSE, warning=FALSE, message=FALSE}
clean_up_ranks(rank_data,params$team) %>%
  make_rank_table(proper_stat_names, type='tm') %>%
  kable(align = 'c')
```

## Predictive Opponent Stats

```{r pred_opp_stats, echo=FALSE, warning=FALSE, message=FALSE}
clean_up_ranks(rank_data, params$team) %>% 
make_rank_table(proper_stat_names, 
                type = 'opp') %>%
  kable(align = 'c')
```

